\myTitle

### 2015-02-10 tex/main-body-text.tex
Added new results from SNP datasets. Some minor additions to the Rscript to make a table of plateau records from FLOCKTURE

\subsection*{{\sc flockture} and {\sc structure}} 
As expected {\sc flockture} and {\sc structure} both perform extremely well on datasets with
well differentiated populations. Infrequently, at higher levels of population differentiation the 
NA-NC and NA-C models in {\sc structure} could be trapped in a local mode resulting in the 
assignment of individuals from two groups into one while individuals from another 
were separated into two populations (Fig.~\ref{fig:FvSdistruct}  Simulation 1). This phenomena 
(only present in the microsatellite datasets) disappears as population differentiation 
declines. As the subtlety of genetic structure 
increased loss for both programs increases and differences among markers emerged.
For the microsatellite dataset we observed that both programs
produce roughtly equivalent results at higher levels of population differentiation. At intermediate 
values, the variance of the loss incurred by each model increases and certain models do marginally
better in assignment. No model does consistently better than the others, until $F_{ST}$ drops 
below 0.0136 after which the loss for {\sc flockture} was markedly larger as was the among run
variance. The drastic increase in variance among runs was also observed with the SNP datasets. 
 {\sc flockture} did, however, have consistenlty smaller loss than  {\sc structure} at high to intermediate 
values of $F_{ST}$. Once $F_{ST}$ fell below 0.016 {\sc structure} began correctly assigning a 
higher proportion of individuals.

The number of plateaus {\sc flockture} encountered and the number of runs that ended on the same plateau quickly 
diminished as the amount of differentiation among populations decreased. For simulations 1-4 a single plateau
greater than 6 was observed in every run. For simulation 5 only a single run yielded a plateau record 
with a single plateau greater than six. For simulations 6 to 11 plateau records of various lengths were observed
but all plateaus were less than 6. No plateaus were observed for datasets 12 through 20. Despite the lack of 
plateaus observed for these datasets graphs of the $q_i$ values were suggestive of population structure within the 
data (Fig.~\ref{fig:FvSdistruct}  Simulation 13). {\sc district} plots of the normalized likelihood values from
{\sc flockture} were consistent and suggestive of population structure within the dataset until simulation 17
after which the majority of the 'best runs' were substantially different in how they clustered individuals.

>>>>

\subsection*{{\sc flockture} and {\sc structure}} 
As expected {\sc flockture} and {\sc structure} both perform extremely well on datasets with
well differentiated populations. Infrequently, at higher levels of population differentiation the 
NA-NC and NA-C models in {\sc structure} could be trapped in a local mode resulting in the 
assignment of individuals from two groups into one while individuals from another 
were separated into two populations (Fig.~\ref{fig:FvSdistruct}  Simulation 1). This phenomena 
(only present in the microsatellite datasets) disappears as population differentiation 
declines. As the subtlety of genetic structure 
increased loss for both programs increases and differences among markers emerged.
For the microsatellite dataset we observed that both programs
produce roughly equivalent results at higher levels of population differentiation. At intermediate 
values, the variance of the loss incurred by each model increases and certain models do marginally
better in assignment. No model did consistently better than others, until $F_{ST}$ drops 
below 0.0136 after which the loss for {\sc flockture} was markedly larger as was the among run
variance. The drastic increase in variance among runs was also observed with the SNP datasets. 
 {\sc flockture} did, however, have consistenlty smaller loss than  {\sc structure} at high to intermediate 
values of $F_{ST}$. Once $F_{ST}$ fell below 0.016 {\sc structure} began correctly assigning a 
higher proportion of individuals.

The number of plateaus {\sc flockture} encountered and the number of runs that ended on the same plateau 
diminished as the amount of differentiation among populations decreased. For the microsatellite datasets
only one run at $F_{ST} = 0.0339$ produced a single plateau of length greater than six. No plateau record had
a length of six or greater at any $F_{ST}$ value greater than 0.0337. Results from the SNP datasets 
were concordant. No runs of {\sc flockture} resulted in a single plateau length of greater than six and
only $F_{ST}$ values greater 0.0323 had plateau records with a plateau greater than six. Despite the lack of 
plateaus observed for many of the simulated datasets graphs of the $q_i$ values were suggestive 
of population structure within the 
data (Fig.~\ref{fig:FvSdistruct}  Simulation 13).
